---
title: "Temperature Comparisons"
author: "Mallory Barnes"
date: "Octobern 10, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(ggplot2)
library(gridExtra)

ggplotRegression <- function(fit){

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  theme(plot.title = element_text(size=8))+
  labs(title = paste("Adj R2 = ",round(signif(summary(fit)$adj.r.squared, 5),3),
                     "Intercept =",round(signif(fit$coef[[1]],5 ),3),
                     " Slope =",round(signif(fit$coef[[2]], 5),3),
                     " P =",round(signif(summary(fit)$coef[2,4], 5))),3)
}

```

### Diurnal Temperature Cycles

RED is Surface Temperature, calculated from radiometer data and modeled emissivity. BLUE is air temperature, measured at the flux towers. 

I've compared the diurnal temperature cycle for estimated Surface Temperature vs. Air Temperature in both winter and summer

*    Differences between air and surface temperature are smaller in summertime than wintertime for the Duke sites, not immediately apparent if it's true for Morgan Monroe too.  

#### Morgan Monroe State Forest
Diurnal temperature signal for winter (January 2008) and summer (July 2008)
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/Mms_hourly_flux.csv")
x$date <- as.Date(x$date)
winter <- subset(x, year==2008 & month==01)
win <- ddply(winter, .(time), summarize, TA = mean(TA, na.rm=TRUE),TS= mean(TS, na.rm=TRUE))
summer <- subset(x, year==2008 & month==07)
sum <- ddply(summer, .(time), summarize, TA = mean(TA, na.rm=TRUE),TS= mean(TS, na.rm=TRUE))
splot <- ggplot(sum, aes(x=time, group=1))+geom_line(aes(y=TA), colour="blue", size=1) + geom_line(aes(y=TS-273.15), colour="red", size=1)+labs(title="Daily summertime temp", y="Temperature (c)",x="Time of Day") +theme_minimal()
  
wplot <- ggplot(win, aes(x=time, group=1))+geom_line(aes(y=TA), colour="blue", size=1) + geom_line(aes(y=TS-273.15), colour="red", size=1)+labs(title="Daily wintertime temp", y="Temperature (c)",x="Time of Day") +theme_minimal()+
  annotate("text", x = 500, y = 5, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=500, y=3, label="Surface Temp", colour="red", fontface="bold")

grid.arrange(wplot, splot, top = "Diurnal Temperature Signal - US-Mms")

```


#### Duke Forest
Diurnal temperature signal for winter (January 2008) and summer (July 2008)
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/Dk230min_flux.csv")
x$date <- as.Date(x$date)
winter <- subset(x, year==2008 & month==01)
win <- ddply(winter, .(time), summarize, TA = mean(TA, na.rm=TRUE),TS= mean(TS, na.rm=TRUE))
summer <- subset(x, year==2008 & month==07)
sum <- ddply(summer, .(time), summarize, TA = mean(TA, na.rm=TRUE),TS= mean(TS, na.rm=TRUE))
splot <- ggplot(sum, aes(x=time, group=1))+geom_line(aes(y=TA), colour="blue", size=1) + geom_line(aes(y=TS-273.15), colour="red", size=1)+labs(title="Daily summertime temp", y="Temperature (c)",x="Time of Day") +theme_minimal()
  
wplot <- ggplot(win, aes(x=time, group=1))+geom_line(aes(y=TA), colour="blue", size=1) + geom_line(aes(y=TS-273.15), colour="red", size=1)+labs(title="Daily wintertime temp", y="Temperature (c)",x="Time of Day") +theme_minimal()+
  annotate("text", x = 500, y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=500, y=6, label="Surface Temp", colour="red", fontface="bold")

grid.arrange(wplot, splot, top = "Diurnal Temperature Signal - US-Dk2")
```

#### Duke Grassland
Diurnal temperature signal for winter (January 2008) and summer (July 2008)
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/Dk130min_flux.csv")
x$date <- as.Date(x$date)
winter <- subset(x, year==2008 & month==01)
win <- ddply(winter, .(time), summarize, TA = mean(TA, na.rm=TRUE),TS= mean(TS, na.rm=TRUE))
summer <- subset(x, year==2008 & month==07)
sum <- ddply(summer, .(time), summarize, TA = mean(TA, na.rm=TRUE),TS= mean(TS, na.rm=TRUE))
splot <- ggplot(sum, aes(x=time, group=1))+geom_line(aes(y=TA), colour="blue", size=1) + geom_line(aes(y=TS-273.15), colour="red", size=1)+labs(title="Daily summertime temp", y="Temperature (c)",x="Time of Day") +theme_minimal()

wplot <- ggplot(win, aes(x=time, group=1))+geom_line(aes(y=TA), colour="blue", size=1) + geom_line(aes(y=TS-273.15), colour="red", size=1)+labs(title="Daily wintertime temp", y="Temperature (c)",x="Time of Day") +theme_minimal()+
  annotate("text", x = 500, y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=500, y=5, label="Surface Temp", colour="red", fontface="bold")

grid.arrange(wplot, splot, top = "Diurnal Temperature Signal - US-Dk1")

```

### Daily Temperature data 

##### Summary Figures 

Morgan Monroe State Forest: 

*   Good agreement between air and surface temperature, surface temperature is consistently warmer. 
*   Gridmet and Daymet both are well correlated to tower air temperature, with only slight a slight bias towards being too cool. 
*   Modis data was very spotty (Indiana is cloudy!) and overestimates temperature by a lot. 
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/mms_temp_comp_10_8.csv")
x$TOB_S <- x$TOB_S -273.15
TaTsplot<-ggplotRegression(lm(Tower_TScor~Tower_TAavg, data = x))
DaymetPlot<-ggplotRegression(lm(Gridmet_Tavg ~Tower_TAavg, data = x))
GridmetPlot <-ggplotRegression(lm(Daymet_Tavg ~Tower_TAavg, data = x))
ModisPlot<-ggplotRegression(lm(Modis_Temp ~TOB_S, data = x))
Modis8dayPlot<-ggplotRegression(lm(Modis_8day_Temp ~TOB_S, data = x))
grid.arrange(TaTsplot, DaymetPlot, GridmetPlot, ModisPlot, Modis8dayPlot, top="Comparisons with Ts and Gridded Products - US-Mms")
```

Duke Forest: 

*   Good agreement between air and surface temperature, surface temperature is consistently warmer, less so than at MMSF. 
*   Daymet is well correlated to tower air temperature, but Gridmet is not predicting tower air temperature well at all. 
*   Modis data had better coverage, bias is improved, but correlation isn't great. 
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/dk2_temp_comp_10_8.csv")
x$TOB_S <- x$TOB_S -273.15
TaTsplot<-ggplotRegression(lm(Tower_TScor~Tower_TAavg, data = x))
DaymetPlot<-ggplotRegression(lm(Gridmet_Tavg ~Tower_TAavg, data = x))
GridmetPlot <-ggplotRegression(lm(Daymet_Tavg ~Tower_TAavg, data = x))
ModisPlot<-ggplotRegression(lm(Modis_Temp~TOB_S, data = x))
Modis8dayPlot<-ggplotRegression(lm(Modis_8day_Temp~TOB_S, data = x))
grid.arrange(TaTsplot, DaymetPlot, GridmetPlot, ModisPlot, Modis8dayPlot, top="Comparisons with Ts and Gridded Products - US-Dk2")
```

Duke Grassland: 

*   Good agreement between air and surface temperature, surface temperature is consistently warmer, more so than at the Duke forest site (!!!) 
*   Daymet is well correlated to tower air temperature, but Gridmet is not predicting tower air temperature well at all. 
*   Modis data had better coverage, but is WAY overestimating temperature and correlation isn't great.

```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/dk1_temp_comp_10_8.csv")
x$TOB_S <- x$TOB_S -273.15
TaTsplot<-ggplotRegression(lm(Tower_TScor~Tower_TAavg, data = x))
DaymetPlot<-ggplotRegression(lm(Gridmet_Tavg ~Tower_TAavg, data = x))
GridmetPlot <-ggplotRegression(lm(Daymet_Tavg ~Tower_TAavg, data = x))
ModisPlot<-ggplotRegression(lm(Modis_Temp ~TOB_S, data = x))
Modis8dayPlot<-ggplotRegression(lm(Modis_8day_Temp ~TOB_S, data = x))
grid.arrange(TaTsplot, DaymetPlot, GridmetPlot, ModisPlot, Modis8dayPlot, top="Comparisons with Ts and Gridded Products - US-Dk1")
```
#### Morgan Monroe State Forest
Daily surface and air temperature, and annual signals for 2008
*Surface temeperature consistently warmer than air temperature, but good agreement.
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/mms_temp_comp_10_8.csv")
x$date <- as.Date(x$date)

all <- ggplot(x, aes(x=date)) + 
  geom_point(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_point(aes(y=Tower_TScor), colour="red", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Tower_TAavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2010-10-05"), y=40, fontface="bold")+
  labs(title="Time Series MMSF", y="Temperature (c)",x="Date") +theme_minimal()

x$year <- substr(as.character(x$date),1,4)
y <- subset(x, year==2008)

for2008 <- ggplot(y, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(y$Tower_TAavg, y$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-08"), y=40, fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Surface Temp", colour="red", fontface="bold")+
    labs(title="Time Series MMSF (2008)", y="Temperature (c)",x="Date") +theme_minimal()

grid.arrange(all, for2008,ncol=1, top="Daily Temperature US-Mms")
```


#### Duke Forest 
Daily surface and air temperature (all) for 2007
*Surface temeperature consistently warmer than air temperature, but good agreement.
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/dk2_temp_comp_10_8.csv")
x$date <- as.Date(x$date)
all <- ggplot(x, aes(x=date)) + 
  geom_point(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_point(aes(y=Tower_TScor), colour="red", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Tower_TAavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40, fontface="bold")+
  labs(title="Time Series Dk2", y="Temperature (c)",x="Date") +theme_minimal()

x$year <- substr(as.character(x$date),1,4)
y <- subset(x, year==2007)

for2007 <- ggplot(y, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(y$Tower_TAavg, y$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2007-10-08"), y=40, fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=3, label="Surface Temp", colour="red", fontface="bold")+
    labs(title="Time Series Dk2 (2007)", y="Temperature (c)",x="Date") +theme_minimal()

grid.arrange(all, for2007,ncol=1, top="Daily Temperature US-Dk2")
```
#### Duke Grassland 
Daily surface and air temperature (all) for 2007
*Surface temeperature consistently warmer than air temperature, but good agreement.
```{r, echo=FALSE, warning=FALSE}
x <- read.csv("C:/Users/malbarn/Documents/Datasets/dk1_temp_comp_10_8.csv")
x$date <- as.Date(x$date)
all <- ggplot(x, aes(x=date)) + 
  geom_point(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_point(aes(y=Tower_TScor), colour="red", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Tower_TAavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40, fontface="bold")+
  labs(title="Time Series Dk1", y="Temperature (c)",x="Date") +theme_minimal()

x$year <- substr(as.character(x$date),1,4)
y <- subset(x, year==2007)

for2007 <- ggplot(y, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(y$Tower_TAavg, y$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2007-10-08"), y=40, fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=3, label="Surface Temp", colour="red", fontface="bold")+
    labs(title="Time Series Dk1 (2007)", y="Temperature (c)",x="Date") +theme_minimal()

grid.arrange(all, for2007,ncol=1, top="Daily Temperature US-Dk1")
```

### Comparisons with gridded datasets
Comparing average daily temperature from tower air and surface temperature, Gridmet, Daymet, MODIS Land Surface temperature.

#### Morgan Monroe 
Comparisons for Morgan Monroe State Forest

Daymet: Good relationship overall
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/mms_temp_comp_10_8.csv")
y$date <- as.Date(y$date)

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2008)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Daymet_Tavg), colour="forestgreen", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Daymet_Tavg, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
  annotate("text", x=as.Date("2008-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Daymet Temp", colour="forestgreen", fontface="bold")+
    labs(title="Daymet vs. Air Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()

r1plot <- ggplotRegression(lm(Daymet_Tavg ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Daymet_Tavg), colour="forestgreen", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Daymet_Tavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
    annotate("text", x=as.Date("2008-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Daymet Temp", colour="forestgreen", fontface="bold")+
  labs(title="Daymet vs. Surface Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()+theme(plot.title = element_text(size=12))

r2plot <- ggplotRegression(lm(Daymet_Tavg ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

Gridmet: Good relationship overall
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/mms_temp_comp_10_8.csv")
y$date <- as.Date(y$date)

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2008)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Gridmet_Tavg), colour="orchid", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Gridmet_Tavg, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
      annotate("text", x=as.Date("2008-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Gridmet Temp", colour="orchid", fontface="bold")+
    labs(title="Gridmet vs. Air Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()

r1plot <- ggplotRegression(lm(Gridmet_Tavg ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Gridmet_Tavg), colour="purple", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Gridmet_Tavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
      annotate("text", x=as.Date("2008-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Gridmet Temp", colour="purple", fontface="bold")+
  labs(title="Gridmet vs. Surface Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()+theme(plot.title = element_text(size=12))

r2plot <- ggplotRegression(lm(Gridmet_Tavg ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

MODIS LST: Very few data points
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/mms_temp_comp_10_8.csv")
y$date <- as.Date(y$date)
y$TOB_S <- y$TOB_S -273.15
y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2008)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=TOB_A), colour="blue", size=0.5) +
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+theme_minimal()+
      annotate("text", x=as.Date("2008-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
    labs(title="MODS LST vs. Air Temp (2008)", y="Temperature (C)",x="Date") 

r1plot <- ggplotRegression(lm(Modis_Temp ~TOB_A, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=TOB_S), colour="red", size=0.5)+
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
        annotate("text", x=as.Date("2008-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
  labs(title="MODIS LST vs. Surface Temp (2008)", y="Temperature (C)",x="Date")+theme(plot.title = element_text(size=12))+theme_minimal()

r2plot <- ggplotRegression(lm(Modis_Temp ~TOB_S, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

#### Duke Forest
Comparisons for Duke Forest

Daymet: Good relationship
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk2_temp_comp_10_8.csv")
y$date <- as.Date(y$date)

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2008)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Daymet_Tavg), colour="forestgreen", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Daymet_Tavg, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
  annotate("text", x=as.Date("2008-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Daymet Temp", colour="forestgreen", fontface="bold")+
    labs(title="Daymet vs. Air Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()

r1plot <- ggplotRegression(lm(Daymet_Tavg ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Daymet_Tavg), colour="forestgreen", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Daymet_Tavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
    annotate("text", x=as.Date("2008-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="Daymet Temp", colour="forestgreen", fontface="bold")+
  labs(title="Daymet vs. Surface Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()+theme(plot.title = element_text(size=12))

r2plot <- ggplotRegression(lm(Daymet_Tavg ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

Gridmet:Worse relationship and consistently underestimates temperature
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk2_temp_comp_10_8.csv")
y$date <- as.Date(y$date)

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2008)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Gridmet_Tavg), colour="orchid", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Gridmet_Tavg, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
      annotate("text", x=as.Date("2008-07-08"), y =5, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=0, label="Gridmet Temp", colour="orchid", fontface="bold")+
    labs(title="Gridmet vs. Air Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()

r1plot <- ggplotRegression(lm(Gridmet_Tavg ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Gridmet_Tavg), colour="purple", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Gridmet_Tavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
      annotate("text", x=as.Date("2008-07-08"), y =5, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=0, label="Gridmet Temp", colour="purple", fontface="bold")+
  labs(title="Gridmet vs. Surface Temperature (2008)", y="Temperature (C)",x="Date") +theme_minimal()+theme(plot.title = element_text(size=12))

r2plot <- ggplotRegression(lm(Gridmet_Tavg ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

MODIS LST: Bias is much better, but relationship as clean as I'd like
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk2_temp_comp_10_8.csv")
y$date <- as.Date(y$date)
y$TOB_S <- y$TOB_S -273.15

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2008)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=TOB_A), colour="blue", size=0.5) +
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+theme_minimal()+
      annotate("text", x=as.Date("2008-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
    labs(title="MODS LST vs. Surface Temp (2008)", y="Temperature (C)",x="Date") 

r1plot <- ggplotRegression(lm(Modis_Temp ~TOB_A, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=TOB_S), colour="red", size=0.5)+
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2008-10-05"), y=40)+
        annotate("text", x=as.Date("2008-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2008-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
  labs(title="MODIS LST vs. Surface Temp (2008)", y="Temperature (C)",x="Date")+theme(plot.title = element_text(size=12))+theme_minimal()

r2plot <- ggplotRegression(lm(Modis_Temp ~TOB_S, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```


#### Duke Grassland 
Comparisons for Duke Grassland
Daymet: Strong Relationship
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk1_temp_comp_10_8.csv")
y$date <- as.Date(y$date)

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2007)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Daymet_Tavg), colour="forestgreen", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Daymet_Tavg, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+
        annotate("text", x=as.Date("2007-07-08"), y =5, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=0, label="Daymet Temp", colour="forest green", fontface="bold")+
    labs(title="Daymet vs. Air Temperature (2007)", y="Temperature (C)",x="Date") +theme_minimal()

r1plot <- ggplotRegression(lm(Daymet_Tavg ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Daymet_Tavg), colour="forestgreen", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Daymet_Tavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+
      annotate("text", x=as.Date("2007-07-08"), y =5, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=0, label="Daymet Temp", colour="forest green", fontface="bold")+
  labs(title="Daymet vs. Surface Temperature (2007)", y="Temperature (C)",x="Date") +theme_minimal()+theme(plot.title = element_text(size=12))

r2plot <- ggplotRegression(lm(Daymet_Tavg ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```
Gridmet: not as clean but bias is acceptable
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk1_temp_comp_10_8.csv")
y$date <- as.Date(y$date)

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2007)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Gridmet_Tavg), colour="orchid", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Gridmet_Tavg, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+
    annotate("text", x=as.Date("2007-07-08"), y =5, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=0, label="Gridmet Temp", colour="orchid", fontface="bold")+
    labs(title="Gridmet vs. Air Temperature (2007)", y="Temperature (C)",x="Date") +theme_minimal()

r1plot <- ggplotRegression(lm(Gridmet_Tavg ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Gridmet_Tavg), colour="purple", size=0.5)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Gridmet_Tavg, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+
    annotate("text", x=as.Date("2007-07-08"), y =5, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=0, label="Gridmet Temp", colour="orchid", fontface="bold")+
  labs(title="Gridmet vs. Surface Temperature (2007)", y="Temperature (C)",x="Date") +theme_minimal()+theme(plot.title = element_text(size=12))

r2plot <- ggplotRegression(lm(Gridmet_Tavg ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

MODIS LST looks pretty good!
```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk1_temp_comp_10_8.csv")
y$date <- as.Date(y$date)
y$TOB_S <- y$TOB_S -273.15

y$year <- substr(as.character(y$date),1,4)
x <- subset(y, year==2007)

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=TOB_A), colour="blue", size=0.5) +
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+theme_minimal()+
      annotate("text", x=as.Date("2007-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
    labs(title="MODS LST vs. Air Temp (2007)", y="Temperature (C)",x="Date") 

r1plot <- ggplotRegression(lm(Modis_Temp ~TOB_A, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=TOB_S), colour="red", size=0.5)+
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+
        annotate("text", x=as.Date("2007-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
  labs(title="MODIS LST vs. Surface Temp (2007)", y="Temperature (C)",x="Date")+theme(plot.title = element_text(size=12))+theme_minimal()

r2plot <- ggplotRegression(lm(Modis_Temp ~TOB_S, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```


```{r, echo=FALSE, warning=FALSE}
y <- read.csv("C:/Users/malbarn/Documents/Datasets/dk1_temp_comp_10_8.csv")
y$date <- as.Date(y$date)
y$year <- substr(as.character(y$date),1,4)
y$month_year <- paste(y$year, substr(as.character(y$date),6,7), sep="-")

ts <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TAavg), colour="blue", size=0.5) +
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TAavg, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+theme_minimal()+
      annotate("text", x=as.Date("2007-07-08"), y =8, label="Air Temp", colour="blue", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
    labs(title="MODS LST vs. Air Temp (2007)", y="Temperature (C)",x="Date") 

r1plot <- ggplotRegression(lm(Modis_Temp ~Tower_TAavg, data = x))


ts2 <- ggplot(x, aes(x=date)) + 
  geom_line(aes(y=Tower_TScor), colour="red", size=0.5)+
  geom_line(aes(y=Modis_Temp), colour="black", size=0.75)+
  annotate("text", label=paste("r=", as.character(round(eval(cor(x$Modis_Temp, x$Tower_TScor, use="complete.obs")),digits=3))), x=as.Date("2007-10-05"), y=40)+
        annotate("text", x=as.Date("2007-07-08"), y =8, label="Surface Temp", colour="red", fontface="bold")+
  annotate("text", x=as.Date("2007-07-08"), y=3, label="MODIS LST", colour="black", fontface="bold")+
  labs(title="MODIS LST vs. Surface Temp (2007)", y="Temperature (C)",x="Date")+theme(plot.title = element_text(size=12))+theme_minimal()

r2plot <- ggplotRegression(lm(Modis_Temp ~Tower_TScor, data = x))

grid.arrange(ts, ts2, r1plot, r2plot)
```

